Flexible Probabilistic Forecasting with Distributional Trees and Forests

### 2020-04-26 pkg/disttree/inst/JSM2018/slides.Rnw
slides for PhD thesis defense
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3011 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 2ac42af760b377bd2d56a4a05978e1eca5f1f0e9
small corrections to adapt for changes and updates in the disttree implementation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3012 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 5622db15384bfba47becde3a04582ef1bfc97701

\setbeamertemplate{caption}{\insertcaption} 
%% includes a replacement for \usepackage{Sweave}
\usepackage{amsmath,tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
\graphicspath{{plots/}}

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<3->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<4->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<4->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x, ytrue, col = pal["forest"], lwd=7)
points(x, y, col = "slategray", pch = 19)
box(lwd = 5)
@

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.2cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_regtree, echo=FALSE, results=hide>>=
## Reg. Tree
set.seed(7)
kappa <- 12
x <- c(1:nobs)/nobs
ytrue <- ytree <- yforest <- numeric(length = length(x))
for(i in 1:nobs) ytrue[i] <- if(x[i]<1/3) 0.5 else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))
y <- ytrue + rnorm(nobs,0,0.3)
for(i in 1:nobs) ytree[i] <- if(x[i]<1/3) 0.5 else {if(x[i]<2/3) 2 else 1}
@
\visible<1->{
<<plot_motivation_regtree, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = ytree, col = pal["forest"], lwd=7)
@
}
\end{center}

\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
 \begin{center}
<<motivation_randforest, echo=FALSE, results=hide>>=
## Random Forest
for(i in 1:nobs) yforest[i] <- if(x[i]<0.27) 0.5 else { if(x[i]<0.39) 0.5 + 1.5*(plogis((x[i]-0.33)/6*700)) else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))}
@
\visible<2->{
<<plot_motivation_randforest, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
@
}
\end{center}

\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
  \visible<3->{
  \begin{center}
  \begin{tikzpicture}
  \draw[line width=0.2mm, black] (0,0) rectangle (2.6,2.24);
  \node[rectangle, align=center] (sq) at (1.3, 1.12) {\Huge{?}};
  \end{tikzpicture}
  \end{center}}
\endminipage

\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<1->{
Regression tree\\
\vspace{0.5cm}
\resizebox{0.3\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n0) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1) at (0.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n1);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2) at (1.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n3) at (1, 0) {};
  \draw[-, line width=1pt] (n2) -- (n3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n4) at (2, 0) {};
  \draw[-, line width=1pt] (n2) -- (n4);
\end{tikzpicture}}
\vspace{0.3cm}\\
\code{rpart}\\
\code{party(kit)}\\
\vspace{1cm}}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<2->{
Random forest\\
\vspace{0.5cm}
\resizebox{0.9\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n00) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n01) at (0.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n01);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n02) at (1.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n02);

@@

  \node[ellipse, fill=HighlightBlue!70, align=center] (n20) at (5, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n21) at (4.5, 1) {};
  \draw[-, line width=1pt] (n20) -- (n21);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n22) at (5.5, 1) {};
  \draw[-, line width=1pt] (n20) -- (n22);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n23) at (5, 0) {};
  \draw[-, line width=1pt] (n22) -- (n23);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n24) at (6, 0) {};
  \draw[-, line width=1pt] (n22) -- (n24);
\end{tikzpicture}
}
\vspace{0.5cm}\\
\code{randomForest}\\
\code{ranger}\\
\code{party(kit)}\\
$\ldots$}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.28\textwidth}
\begin{center}
\vspace{0.68cm}
\visible<3->{
Distributional trees and forests\\
\vspace{1.7cm}
\code{disttree}\\
based on \code{partykit}\\
\vspace{1cm}}
\end{center}
\endminipage
\end{figure}
\end{frame}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 type.tree = "ctree", ntree = 100, censtype = "left", censpoint = 0,
                 control = ctree_control(teststat = "quad", testtype = "Univ",
                                         intersplit = TRUE,
                                         mincriterion = 0, minsplit = 50,
                                         minbucket = 20), mtry = 27)

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.2cm}
\textbf{Application for one station:}
\begin{itemize}
\item Learn forest model on data from 24 years.
\item Evaluate on 4 years.
\item 10 times 7-fold cross validation.
\item Compare to commonly used heteroscedastic censored Gaussian models:
\end{itemize}
%\begin{itemize}
%\item Prespecified GAM: variable selection based on meteorological expert knowledge.
%\item Boosted GAM: automatic variable selection.
%\item Ensemble Model Output Statistics (EMOS): linear predictors using only total precipitation predictions as covariates.
%\end{itemize}
\vspace{0.1cm}
\begin{table}[t!]
\footnotesize

\hskip-0.4cm\begin{tabular}{ l l l }
\hline
Model & Type & Variable Selection \\
\hline
\vspace{-0.15cm}
\textbf{Distributional forest} & recursive    & automatic \\ 
                               & partitioning &           \\ 
\hline
\vspace{-0.15cm}
\textbf{Prespecified GAM} & spline  & based on expert \\
                          & in each & knowledge      \\
\hline
\vspace{-0.15cm}
\textbf{Boosted GAM} & spline  & automatic  \\
                     & in each &            \\
\hline
\vspace{-0.15cm}
\textbf{EMOS} & linear & total precipitation mean \\
              &        & and standard deviation   \\
\hline
\end{tabular}
\end{table}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.2cm}
\textbf{Application for all 95 stations:}
\begin{itemize}
\item Learn forest model on data from 24 years (1985--2008).
\item Evaluate on 4 years (2009--2012).
\item Compare to commonly used heteroscedastic censored Gaussian models. %:\\
\end{itemize}
%\begin{itemize}
%\item Prespecified GAM: variable selection based on meteorological expert knowledge.
%\item Boosted GAM: automatic variable selection.
%\item Ensemble Model Output Statistics (EMOS): linear predictors using only total precipitation predictions as covariates.
%\end{itemize}

%\vspace{0.1cm}
%\begin{table}[t!]
%\footnotesize
%\nodindent
%\hskip-0.4cm\begin{tabular}{ l l l }
%\hline
%Model & Type & Variable Selection \\
%\hline
%\vspace{-0.15cm}
%\textbf{Forest} & recursive    & automatic \\ 
%                & partitioning &           \\ 
%\hline
%\vspace{-0.15cm}
%\textbf{prespecified GAM} & spline  & based on expert \\
%                          & in each & knowledge      \\
%\hline
%\vspace{-0.15cm}
%\textbf{boosted GAM} & spline  & automatic  \\
%                     & in each &            \\
%\hline
%\vspace{-0.15cm}
%\textbf{EMOS} & linear & total precipitation mean \\
%              &        & and standard deviation   \\
%\hline
%\end{tabular}
%\end{table}
\end{frame}

>>>>

\setbeamertemplate{caption}{\insertcaption} 
%% includes a replacement for \usepackage{Sweave}
% \usepackage{Sweave}
\usepackage{amsmath,tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
\graphicspath{{plots/}}

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.285\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.285\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<3->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<4->{{\LARGE$\rightarrow$}}
\minipage{0.285\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<4->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x, ytrue, col = pal["forest"], lwd=7)
points(x, y, col = "slategray", pch = 19)
box(lwd = 5)
@

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.2cm}
\begin{figure}[!htb]
\minipage{0.285\textwidth}
\begin{center}
<<motivation_regtree, echo=FALSE, results=hide>>=
## Reg. Tree
set.seed(7)
kappa <- 12
x <- c(1:nobs)/nobs
ytrue <- ytree <- yforest <- numeric(length = length(x))
for(i in 1:nobs) ytrue[i] <- if(x[i]<1/3) 0.5 else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))
y <- ytrue + rnorm(nobs,0,0.3)
for(i in 1:nobs) ytree[i] <- if(x[i]<1/3) 0.5 else {if(x[i]<2/3) 2 else 1}
@
\visible<1->{
<<plot_motivation_regtree, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = ytree, col = pal["forest"], lwd=7)
@
}
\end{center}

\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.285\textwidth}
 \begin{center}
<<motivation_randforest, echo=FALSE, results=hide>>=
## Random Forest
for(i in 1:nobs) yforest[i] <- if(x[i]<0.27) 0.5 else { if(x[i]<0.39) 0.5 + 1.5*(plogis((x[i]-0.33)/6*700)) else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))}
@
\visible<2->{
<<plot_motivation_randforest, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
@
}
\end{center}

\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.285\textwidth}
  \visible<3->{
  \begin{center}
  \begin{tikzpicture}
  \draw[line width=0.2mm, black] (0,0) rectangle (2.44,2.12);
  \node[rectangle, align=center] (sq) at (1.22, 1.06) {\Huge{?}};
  \end{tikzpicture}
  \end{center}}
\endminipage

\minipage{0.285\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<1->{
Regression tree\\
\vspace{0.5cm}
\resizebox{0.3\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n0) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1) at (0.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n1);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2) at (1.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n3) at (1, 0) {};
  \draw[-, line width=1pt] (n2) -- (n3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n4) at (2, 0) {};
  \draw[-, line width=1pt] (n2) -- (n4);
\end{tikzpicture}}
\vspace{0.3cm}\\
\code{rpart}\\
\code{party(kit)}\\
\vspace{1cm}}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.285\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<2->{
Random forest\\
\vspace{0.5cm}
\resizebox{0.9\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n00) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n01) at (0.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n01);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n02) at (1.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n02);

@@

  \node[ellipse, fill=HighlightBlue!70, align=center] (n20) at (5, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n21) at (4.5, 1) {};
  \draw[-, line width=1pt] (n20) -- (n21);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n22) at (5.5, 1) {};
  \draw[-, line width=1pt] (n20) -- (n22);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n23) at (5, 0) {};
  \draw[-, line width=1pt] (n22) -- (n23);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n24) at (6, 0) {};
  \draw[-, line width=1pt] (n22) -- (n24);
\end{tikzpicture}
}
\vspace{0.5cm}\\
\code{randomForest}\\
\code{ranger}\\
\code{party(kit)}\\
$\ldots$}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.285\textwidth}
\begin{center}
\vspace{0.68cm}
\visible<3->{
Distributional trees and forests\\
\vspace{1.7cm}
\code{disttree}\\
based on \code{partykit}\\
\vspace{1cm}}
\end{center}
\endminipage
\end{figure}
\end{frame}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 ntree = 100, censtype = "left", censpoint = 0,
                 control = disttree_control(type.tree = "ctree",
                                            teststat = "quad", testtype = "Univ",
                                            intersplit = TRUE,
                                            mincriterion = 0, minsplit = 50,
                                            minbucket = 20), mtry = 27)

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.2cm}
\textbf{Application for one station:}
\begin{itemize}
\item Learn forest model on data from 24 years.
\item Evaluate on 4 years.
\item 10 times 7-fold cross validation.
\item Compare to commonly used heteroscedastic censored Gaussian models:
\end{itemize}
%\begin{itemize}
%\item Prespecified GAMLSS: variable selection based on meteorological expert knowledge.
%\item Boosted GAMLSS: automatic variable selection.
%\item Ensemble Model Output Statistics (EMOS): linear predictors using only total precipitation predictions as covariates.
%\end{itemize}
\vspace{0.1cm}
\begin{table}[t!]
\footnotesize

\hskip-0.4cm\begin{tabular}{ l l l }
\hline
Model & Type & Variable Selection \\
\hline
\vspace{-0.15cm}
\textbf{Distributional forest} & recursive    & automatic \\ 
                               & partitioning &           \\ 
\hline
\vspace{-0.15cm}
\textbf{Prespecified GAMLSS} & spline  & based on expert \\
                          & in each & knowledge      \\
\hline
\vspace{-0.15cm}
\textbf{Boosted GAMLSS} & spline  & automatic  \\
                     & in each &            \\
\hline
\vspace{-0.15cm}
\textbf{EMOS} & linear & total precipitation mean \\
              &        & and standard deviation   \\
\hline
\end{tabular}
\end{table}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.2cm}
\textbf{Application for all 95 stations:}
\begin{itemize}
\item Learn forest model on data from 24 years (1985--2008).
\item Evaluate on 4 years (2009--2012).
\item Compare to commonly used heteroscedastic censored Gaussian models. %:\\
\end{itemize}
%\begin{itemize}
%\item Prespecified GAMLSS: variable selection based on meteorological expert knowledge.
%\item Boosted GAMLSS: automatic variable selection.
%\item Ensemble Model Output Statistics (EMOS): linear predictors using only total precipitation predictions as covariates.
%\end{itemize}

%\vspace{0.1cm}
%\begin{table}[t!]
%\footnotesize
%\nodindent
%\hskip-0.4cm\begin{tabular}{ l l l }
%\hline
%Model & Type & Variable Selection \\
%\hline
%\vspace{-0.15cm}
%\textbf{Forest} & recursive    & automatic \\ 
%                & partitioning &           \\ 
%\hline
%\vspace{-0.15cm}
%\textbf{Prespecified GAMLSS} & spline  & based on expert \\
%                          & in each & knowledge      \\
%\hline
%\vspace{-0.15cm}
%\textbf{Boosted GAMLSS} & spline  & automatic  \\
%                     & in each &            \\
%\hline
%\vspace{-0.15cm}
%\textbf{EMOS} & linear & total precipitation mean \\
%              &        & and standard deviation   \\
%\hline
%\end{tabular}
%\end{table}
\end{frame}

### 2020-04-26 pkg/disttree/inst/MIP-Seminar/slides.Rnw
slides for PhD thesis defense
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3011 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 2ac42af760b377bd2d56a4a05978e1eca5f1f0e9
small corrections to adapt for changes and updates in the disttree implementation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3012 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 5622db15384bfba47becde3a04582ef1bfc97701

\setbeamertemplate{caption}{\insertcaption} 
%% includes a replacement for \usepackage{Sweave}
\usepackage{changepage}
\usepackage{amsmath,tikz}
\usepackage{calc}
\usepackage{graphicx}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap,trees,tikzmark,decorations.pathreplacing}
\graphicspath{{plots/}}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 type.tree = "ctree", ntree = 100, censtype = "left", censpoint = 0,
                 control = ctree_control(teststat = "quad", testtype = "Univ",
                                         intersplit = TRUE,
                                         mincriterion = 0, minsplit = 50,
                                         minbucket = 20), mtry = 27)

>>>>

\setbeamertemplate{caption}{\insertcaption} 
%% includes a replacement for \usepackage{Sweave}
\usepackage{Sweave}
\usepackage{changepage}
\usepackage{amsmath,tikz}
\usepackage{calc}
\usepackage{graphicx}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap,trees,tikzmark,decorations.pathreplacing}
\graphicspath{{plots/}}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 type.tree = "ctree", ntree = 100, censtype = "left", censpoint = 0,
                 control = disttree_control(type.tree = "ctree", 
                                            teststat = "quad", testtype = "Univ",
                                            intersplit = TRUE,
                                            mincriterion = 0, minsplit = 50,
                                            minbucket = 20), mtry = 27)

### 2020-04-26 pkg/disttree/inst/eeecon_workshop/slides.Rnw
slides for PhD thesis defense
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3011 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 2ac42af760b377bd2d56a4a05978e1eca5f1f0e9
small corrections to adapt for changes and updates in the disttree implementation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3012 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 5622db15384bfba47becde3a04582ef1bfc97701

\vspace{-3.5cm}
\visible<6->{
\textbf{Application/Motivation:}
\begin{itemize}
\item Prediction.
\item Capturing dependencies and interactions.
\end{itemize}
}
\vspace{0.5cm}
\visible<7->{
\textbf{Two main approaches / ``cultures'':}
\begin{itemize}
\item Data modeling.
\item Algorithmic modeling.
\end{itemize}
}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.1cm}
\textbf{Idea:} Statistical model with numerical predictions as covariates.\\
\vspace{0.4cm}
\textbf{Distribution assumption:}\\
\vspace{-0.25cm}
$$(\text{precipitation})^\frac{1}{1.6} \sim \textit{c}\mathcal{N}(\mu,\sigma^2) \quad \text{censored at 0.}$$
%\vspace{2cm}
\visible<2->{
\textbf{Data:}
%\vspace{-1cm}
\begin{itemize}
\item \textbf{Y:} Observation data (National Hydrographical Service):\\
\begin{itemize}
\item 95 observation stations in Tyrol, Austria.\\
\item Daily 24h precipitation sums (July, 1985--2012).
%\item Daily 24h precipitation sums from July over 28 years (1985--2012).
\end{itemize}
\vspace{0.1cm}
\item \textbf{X:} NWP model output (Global Ensemble Forecast System):\\
\vspace{0.14cm}
\quad \small{Ensemble predictions of various meteorological quantities\\
\quad (precipitation, temperature, air pressure, sunshine, \dots)\\
\quad $\rightarrow$ 80 covariates.}
\end{itemize}
}
\end{frame}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 type.tree = "ctree", ntree = 100, censtype = "left", censpoint = 0,
                 control = ctree_control(teststat = "quad", testtype = "Univ",
                                         intersplit = TRUE,
                                         mincriterion = 0, minsplit = 50,
                                         minbucket = 20), mtry = 27)

>>>>

\vspace{-3.5cm}
\visible<6->{
\textbf{Application / Motivation:}
\begin{itemize}
\item Prediction.
\item Capturing dependencies and interactions.
\end{itemize}
}
\vspace{0.5cm}
\visible<7->{
\textbf{Two main approaches / ``cultures'':}
\begin{itemize}
\item Data modeling.
\item Algorithmic modeling.
\end{itemize}
}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace{0.1cm}
\textbf{Idea:} Statistical model with numerical predictions as covariates.\\
\vspace{0.4cm}
\textbf{Distribution assumption:}\\
\vspace{-0.25cm}
$$(\text{precipitation})^\frac{1}{1.6} \sim \textit{c}\mathcal{N}(\mu,\sigma^2) \quad \text{censored at 0.}$$
%\vspace{2cm}
\visible<2->{
\textbf{Data:}
%\vspace{-1cm}
\begin{itemize}
\item \textbf{Y:} Observation data (National Hydrographical Service):\\
\begin{itemize}
\item Daily 24h precipitation sums (July, 1985--2012).\\
\item 95 observation stations in Tyrol, Austria.
\end{itemize}
\vspace{0.1cm}
\item \textbf{X:} NWP model output (Global Ensemble Forecast System):\\
\vspace{0.14cm}
\quad \small{Ensemble predictions of various meteorological quantities\\
\quad (precipitation, temperature, air pressure, sunshine, \dots)\\
\quad $\rightarrow$ 80 covariates.}
\end{itemize}
}
\end{frame}

@@

df <- distforest(df.formula, data = learndata, family = dist_list_cens_normal, 
                 ntree = 100, censtype = "left", censpoint = 0,
                 control = disttree_control(type.tree = "ctree", ,
                                            teststat = "quad", testtype = "Univ",
                                            intersplit = TRUE,
                                            mincriterion = 0, minsplit = 50,
                                            minbucket = 20), mtry = 27)
